---
title: "EDS 221 Day 5 Notes Lecture + Computational"
author: "Dalila Lara"
date: "2022-08-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(testthat)
```

# Lecture 9 Functions
Unit Test: 
Formal automated check to make sure a piece ("unit") of your code is behaving expectedly 

testthat::
Provides functions to easily descive what the function needs to do and catches, erros, messages, and warnings
  - expect_equal() does function return expected values
  - expect_type() does it return expected type
  - expect_length() retun length
  - expect_true() function return TRUE

```{r}
# Can run `testthat` function to see if value output runs as shoould
fish_mass <- function(alpha, beta, fish_length) {
if (fish_length <= 0) {
stop("Fish length must be greater than 0.")
}
mass <- alpha * (fish_length ^ beta)
}

#test example
expect_length(fish_mass(alpha = 1, beta = 2, fish_length = 3), 1)
# we expect the length to be returned of vector
# for fish_mass to be evaluated at these values
# to equal 1
```


